\documentclass[10pt,twoside]{article}

\usepackage{a4}
\usepackage[obeyspaces]{url}
\usepackage{graphicx}
\usepackage{hevea}
\usepackage{fancyvrb}

\def\section{\@startsection{section}{1}
{\z@}{-2.5ex plus -0.5ex minus -0.1ex}{0.5ex plus 0.1ex}{\large\bf}}
\def\subsection{\@startsection{subsection}{2}
{\z@}{-2.25ex plus -0.3ex minus -0.2ex}{0.05ex plus 0.05ex}{\normalsize\bf}}
\def\subsubsection{\@startsection{subsubsection}{3}
{\z@}{-2.25ex plus -0.3ex minus -0.2ex}{0.05ex plus 0.05ex}{\normalsize\sc}}
\def\paragraph{\@startsection{paragraph}{4}
{\z@}{2ex plus 0.5ex minus 0.1ex}{-0.7em}{\normalsize\it}}

\def\@listi{\topsep 0.4ex \parsep 0pt \itemsep \parsep}
\topsep 0.4ex \partopsep 0pt \itemsep 0pt \parsep 0pt
\def\@listii{\leftmargin\leftmarginii
 \labelwidth\leftmarginii\advance\labelwidth-\labelsep
 \topsep 0pt \parsep 0pt \itemsep \parsep}
\def\@listiii{\leftmargin\leftmarginiii
 \labelwidth\leftmarginiii\advance\labelwidth-\labelsep
 \parsep \z@ \topsep 0pt \partopsep 0pt \itemsep \topsep}

\setcounter{tocdepth}{1}
\setcounter{cuttingdepth}{1}
\ifhevea
\newcommand{\l}{l}
\newcommand{\vfill}{}
\tocnumber
\htmlprefix{Globule User Manual: }
\newenvironment{p}{}{\par}
\clubpenalty=10000
\widowpenalty=10000
\fi

\title{Issues and Troubleshooting Guide}
\date{Version 1.3.0
  \ifhevea \begin{rawhtml}</H3> 
<H3 ALIGN=center>\end{rawhtml} \else \\ \fi
  \ahrefurl{http://www.globule.org/}}
\author{\ahref{\url{http://www.halderen.net/}}{Berry~van~Halderen}}

\begin{document}
\maketitle

\tableofcontents
\cleardoublepage

\parindent 0pt
\parskip 1em

\section{Introduction}

This document describes some more and less common issues on installing,
configuring and using Globule, which are not classified as bugs or
erroneous operation of Globule/Apache.

This document is rather unstructured, as it sometimes handles multiple and
relates issues at the same time.

\section{Issues regarding installation}

\subsection*{Installer doesn't work.}

\begin{itemize}
\item Check that you aren't running the installer.sh from the same directory
as you want to install the globule system to.

The installer script clears out the destination directory.

\item Check out that your TMP and TMPDIR environment variables aren't set to a (sub)directory of your installation destination directory.

The installer script clears out the destination directory.  Configure scripts
aren't able to run without a temporary scratch directory.

\end{itemize}

\item Guillaume's laptop hasn't got bison/lex/flex nor curl needed for php

if [ "$TMP" = "$HOME/tmp" -o "$TMPDIR" = "$HOME/tmp" ]; then
  echo "cannot work with this setup"
else
  cd /tmp
  wget -O installer.sh 'http://world.cs.vu.nl/pub/globule/installer.sh'
  chmod u+x installer.sh
  ./installer --keep-build --extra-php-config="--disable-dba" 2>&1
  | tee installer.log
fi

./configure --prefix=/home/berry --with-apxs2filter=/home/berry/bin/apxs --disable-cgi --enable-safe-mode --with-gd=/home/berry --with-curl=/home/berry --with-mysql=/home/berry --with-mysqli=/home/berry/bin/mysql_config --with-mysql-sock=/home/berry/var/mysql.sock --disable-static --disable-dbase --disable-dba

--disabel-dba doesn't work, option has to be removed from installer.sh
